%%\begin{itemize}
%%\item I would follow the path of the abstract, we should probably provide some numbers and info on storm
%%\item mind you we should stress on the innovative aspects of the paper and tech. there is nothing strictly related to it
%%\item we should comment on what could be done with OSTIA in combination with Eclipse Based tech.
%%\end{itemize}
%%%Big data architectures have been gaining momentum in the last few years. For example, Twitter uses complex Stream topologies featuring frameworks like Storm to analyse and learn trending topics from billions of tweets per minute. However, verifying the consistency of said topologies often requires de- ployment on multi-node clusters and can be expensive as well as time consuming. As an aid to designers and developers evaluating their Stream topologies at design-time, we developed OSTIA, that is, ?On-the-fly Storm Topology Inference Analysis?. OSTIA allows reverse-engineering of Storm topologies so that designers and developers may: (a) use previously existing model- driven verification&validation techniques on elicited models; (b) visualise and evaluate elicited models against consistency checks that would only be available at deployment and run-time. We illustrate the uses and benefits of OSTIA on three real-life industrial case studies.
%%%%%%
%%%%%% intro needs a bit of refinement with what we say in the title and a few more definitions should be included (e.g., about streaming and what it represents or why topologies ?are? the Big Data architecture)? Perhaps we should also increase the stress and focus on Quality and deployability aspects (i.e., the main topics of next year?s QoSA) in the intro, and how OSTIA aids at improving these aspects

Big data applications process vast amounts of data \cite{bdsurvey} for the purpose of gaining key business intelligence through complex analytics such as machine-learning \cite{ml4bd}. Said applications are receiving increased attention in the last few years given their ability to yield competitive advantage by direct investigation of user needs and trends hidden in the enormous quantities of data produced daily by the average internet user. Gartner predicts\footnote{\url{http://www.gartner.com/newsroom/id/2637615}} that said business intelligence and analytics applications will remain top focus for CIOs until at least 2017-2018. 
However, there are many costs and complexities behind harnessing said applications ranging from very high infrastructure costs to steep learning curves for the many frameworks involved in designing and developing applications for Big data, e.g., Apache Storm\footnote{\url{http://storm.apache.org/}}, Apache Spark\footnote{\url{http://spark.apache.org/}} or Hadoop\footnote{\url{https://hadoop.apache.org/}} to name a few.

In our own experience with designing and developing for Big Data, we observed that a key complexity lies in quickly and continuously evaluating the effectiveness of big-data architectures, or better, \emph{topologies} - in the Big data jargon. Effectiveness in Big data terms means being able to design, deploy, operate, refactor and then (re-)deploy architectures/topologies continuously and consistently with runtime restrictions of necessary Big-data frameworks involved (e.g., Spark, Storm, etc.). A very trivial example of said restrictions consists in the need for the topology to represent a Directed-Acyclic-Graph (DAG), a key constraint of the Storm and Spark frameworks.
%\textbf{TODO: can we add an example of said consistency checks/issues?} \\
We argue that such effectiveness can be maintained starting from design time, by enacting a continuous architecting of big-data topologies consistently with a DevOps organisational structure \cite{ossslr,devops}. Supporting this effectiveness at design time eases the (re-)deployability of Big data topologies and save the time and effort to run trial-and-error experiments on expensive infrastructure.

To sustain this argument, we developed OSTIA, that stands for: ``On-the-fly Static Topology Inference Analysis". OSTIA allows designers and developers to infer the application topology though on-the-fly reverse-engineering and architecture recovery \cite{archrec}. During this inference step, OSTIA analyses the operating topology to make sure it is consistent with restrictions and constraints of the Big data frameworks at hand. Also, in an effort to tackle said complexities and offer support in a DevOps fashion, OSTIA was engineered to act as a mechanism that closes the feedback loop between operating Streaming topologies (-Ops phase) and their development and improvement phase (Dev- phase).

Currently, OSTIA focuses on Storm, i.e., one of the most famous and established real-time stream processing Big data engine \cite{storm}. OSTIA hardcodes intimate knowledge on the streaming development framework (Storm, in our case) and its dependence structure in the form of a meta-model \cite{mda}. This knowledge is necessary to make sure that elicited topologies are correct, so that models may be used in at least four scenarios: (a) realising an exportable visual representation for said topologies; (b) checking said topologies against framework restrictions that would only become evident during infrastructure setup or runtime operation; (c) checking that said topologies do not show any anti-patterns \cite{patternoriented2000} that may lower performance and limit deployability/executability; (d) finally, use said topologies for further analysis, e.g., through model verification \cite{icsoft}.

This paper outlines OSTIA, elaborating its major usage scenarios and its benefits while discussing and addressing its limitations. Also, we evaluate OSTIA using industrial case-study research featuring an open-source social-sensing application to show that OSTIA yields valuable design and development insights using an inference analysis of the three static topologies behind said industrial application. Finally, we elaborate on how OSTIA helps the continuous architecting of recovered topologies by means of valuable on-the-fly analyses as well as ancillary verification techniques. We conclude that OSTIA does in fact provide valuable insights for software architects to continuously architect and increase quality of their Big-data design and development featuring Storm so that expedite (re-)deployment can take place.

The rest of the paper is structured as follows. Section \ref{ra} outlines our research problem, research questions and our approach at tackling them. Sections \ref{rs}, \ref{sec:anti-pattern} and \ref{algo} outline OSTIA, discussing the usage scenarios and (anti-)patterns it was designed to support while outlining the main benefits we perceived in using it. Section \ref{eval} elaborates further on the benefits by providing an actual evaluation of OSTIA using three cases from industrial practice. Section \ref{disc} discusses the results and evaluation, also outlining OSTIA limitations and potential threats to its validity. Finally, Sections \ref{rw} and \ref{conc} outline related work and conclude the paper.